How functional traits influence plant growth and shade tolerance across the life-cycle

### 2018-05-01 ms/ms-supp.Rnw
Tweaks for technical check from journal

\documentclass[9pt,onecolumn,twoside]{pnas-new}
% Use the lineno option to display guide line numbers if required.
% Note that the use of elements such as single-column equations
% may affect the guide line number alignment.

\templatetype{pnasresearcharticle}

\title{
{\normalfont \fontsize{12pt}{16pt}
{\color{black50} Supporting information for:}\\} \vskip6pt
\fontsize{16pt}{20pt} How functional traits influence plant growth and shade tolerance across the life-cycle
}

@@

% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
\author[a,1]{Daniel S. Falster}
\author[b]{Remko A. Duursma}
\author[c]{Richard G. FitzJohn}

% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
\affil[a]{Evolution \& Ecology Research Centre, and School of Biological, Earth and
Environmental Sciences, University of New South Wales, Sydney NSW 2052, Australia}
\affil[b]{Hawkesbury Institute for the Environment, Western Sydney University, Locked Bag 1797, Penrith NSW 2751, Australia}
\affil[c]{Imperial College, London, United Kingdom}

% Please give the surname of the lead author for the running footer
\leadauthor{Falster}

\dates{This supplement was compiled on \today}
\doi{\url{www.pnas.org/cgi/doi/10.1073/pnas.XXXXXXXXXX}}

\hypersetup{
     linkcolor=pnasbluetext
}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

@@

\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}
\renewcommand{\theequation}{S\arabic{equation}}
\renewcommand{\thesection}{S\arabic{section}}

\section{Additional details on the \texttt{FF16} growth model in the {\plant} package}

@@

\subsection{Hyper-parameterisation of the \texttt{FF16} model via traits}

@@

\subsubsection{Seed mass}

@@

\subsubsection{Nitrogen per unit leaf area}

@@

\subsubsection{Leaf mass per unit area}

@@

\subsubsection{Wood density}

@@

\subsubsection{Implementation of hyper-parameterisation function}

@@

\section{References}
\bibliography{references}

\section{Supporting Tables and Figures}\label{app:supp_info_table}

% latex table generated in R 3.4.0 by xtable 1.8-2 package
% Thu Apr  5 13:08:59 2018
\begin{table*}[ht]
\centering
\caption{Core parameter of the 	exttt{FF16} physiological model.} 
\label{tab:params_core}
\begin{tabular}{p{7cm}llll}
  \hline
Description & Symbol & Unit & Code & Value \\ 
  \hline
\textbf{Plant construction} &  &  &  &  \\ 
  Crown-shape parameter & $\eta$ &  & \texttt{eta} & 12 \\ 
  Leaf mass per area & $\phi$ & $\mathrm{kg}\,\mathrm{m}^{-2}$ & \texttt{lma} & 0.1978791 \\ 
  Wood density & $\rho$ & $\mathrm{kg}\,\mathrm{m}^{-3}$ & \texttt{rho} & 608 \\ 
  Sapwood area per unit leaf area & $\theta$ &  & \texttt{theta} & 0.0002141786 \\ 
  Height of plant with leaf area of 1m$^2$ & $\alpha_{\rm l1}$ & m & \texttt{a\_l1} & 2.17 \\ 
  Exponent of relationship between height and leaf area & $\alpha_{\rm l2}$ &  & \texttt{a\_l2} & 0.5 \\ 
  Root mass per unit leaf area & $\alpha_{\rm r1}$ & $\mathrm{kg}\,\mathrm{m}^{-2}$ & \texttt{a\_r1} & 0.07 \\ 
  Ratio of bark area to sapwood area & $\alpha_{\rm b1}$ &  & \texttt{a\_b1} & 0.17 \\ 
  \textbf{Production} &  &  &  &  \\ 
  Leaf photosynthesis per area & $\alpha_{\rm p1}$ & $\mathrm{mol}\,\mathrm{yr}^{-1}\,\mathrm{m}^{-2}$ & \texttt{a\_p1} & 151.1778 \\ 
  Saturation of leaf photosynthesis per area & $\alpha_{\rm p2}$ &  & \texttt{a\_p2} & 0.2047162 \\ 
  Yield = fraction of carbon fixed converted into mass & $\alpha_{\rm y}$ &  & \texttt{a\_y} & 0.7 \\ 
  Biomass per mol carbon & $\alpha_{\rm bio}$ & $\mathrm{kg}\,\mathrm{mol}^{-1}$ & \texttt{a\_bio} & 0.0245 \\ 
  Leaf respiration per mass & $r_{\rm l}$ & $\mathrm{mol}\,\mathrm{yr}^{-1}\,\mathrm{kg}^{-1}$ & \texttt{r\_l} & 198.4545 \\ 
  Fine-root respiration per mass & $r_{\rm r}$ & $\mathrm{mol}\,\mathrm{yr}^{-1}\,\mathrm{kg}^{-1}$ & \texttt{r\_r} & 217 \\ 
  Sapwood respiration per mass & $r_{\rm s}$ & $\mathrm{mol}\,\mathrm{yr}^{-1}\,\mathrm{kg}^{-1}$ & \texttt{r\_s} & 6.598684 \\ 
  Bark respiration per mass & $r_{\rm b}$ & $\mathrm{mol}\,\mathrm{yr}^{-1}\,\mathrm{kg}^{-1}$ & \texttt{r\_b} & 13.19737 \\ 
  Turnover rate for leaves & $k_{\rm l}$ & $\mathrm{yr}^{-1}$ & \texttt{k\_l} & 0.1521952 \\ 
  Turnover rate for sapwood & $k_{\rm s}$ & $\mathrm{yr}^{-1}$ & \texttt{k\_s} & 0.2 \\ 
  Turnover rate for bark & $k_{\rm b}$ & $\mathrm{yr}^{-1}$ & \texttt{k\_b} & 0.2 \\ 
  Turnover rate for fine roots & $k_{\rm r}$ & $\mathrm{yr}^{-1}$ & \texttt{k\_r} & 1 \\ 
  \textbf{Fecundity} &  &  &  &  \\ 
  Seed mass & $\omega$ & kg & \texttt{omega} & 0.000038 \\ 
  Height at maturation & $H_{{\rm mat}}$ & m & \texttt{hmat} & 15 \\ 
  Maximum allocation to reproduction & $\alpha_{\rm f1}$ &  & \texttt{a\_f1} & 0.8 \\ 
  Parameter determining rate of change in $r(x, m_\textrm{l})$ around $H_{\rm mat}$ & $\alpha_{\rm f2}$ &  & \texttt{a\_f2} & 10 \\ 
   \hline
\end{tabular}
\end{table*}

% latex table generated in R 3.4.0 by xtable 1.8-2 package
% Thu Apr  5 13:08:59 2018
\begin{table*}[ht]
\centering
\caption{Parameters for hyper-parameterisation of the \texttt{FF16} physiological model.} 
\label{tab:params_hyper}
\begin{tabular}{p{9cm}llll}
  \hline
Description & Symbol & Unit & Code & Value \\ 
  \hline
\textbf{Leaf turnover} &  &  &  &  \\ 
  Global average leaf mass per area & $\phi_0$ & $\mathrm{kg}\,\mathrm{m}^{-2}$ & \texttt{lma\_0} & 0.1978791 \\ 
  Rate of leaf turnover at average leaf mass per unit leaf area, $\phi_0$ & $\beta_{\rm kl1}$ & $\mathrm{yr}^{-1}$ & \texttt{B\_kl1} & 0.4565855 \\ 
  Scaling exponent for $\phi$ in leaf turnover & $\beta_{\rm kl2}$ &  & \texttt{B\_kl2} & 1.71 \\ 
  \textbf{Sapwood turnover} &  &  &  &  \\ 
  Global average wood density & $\rho_0$ & $\mathrm{kg}\,\mathrm{m}^{-3}$ & \texttt{rho\_0} & 608 \\ 
  Rate of sapwood turnover at average wood density, $\rho_0$ & $\beta_{\rm ks1}$ & $\mathrm{yr}^{-1}$ & \texttt{B\_ks1} & 0.2 \\ 
  Scaling exponent for $\rho$ in sapwood turnover & $\beta_{\rm ks2}$ &  & \texttt{B\_ks2} & 1.25 \\ 
  \textbf{Photosynthesis} &  &  &  &  \\ 
  Leaf nitrogen per unit leaf area & $\nu$ & $\mathrm{kg}\,\mathrm{m}^{-2}$ & \texttt{narea} & 0.00187 \\ 
  Global average nitrogen per unit leaf area & $\nu_0$ & $\mathrm{kg}\,\mathrm{m}^{-2}$ & \texttt{narea\_0} & 0.00187 \\ 
  Potential CO$_2$ photosynthesis at average leaf nitrogen, $\nu_0$ & $\beta_{\rm lf1}$ & $\mathrm{mol}\,\mathrm{d}^{-1}\,\mathrm{m}^{-2}$ & \texttt{B\_lf1} & 0.8273474 \\ 
  Curvature of light response curve & $\beta_{\rm lf2}$ &  & \texttt{B\_lf2} & 0.75 \\ 
  Quantum yield of leaf photosynthesis (CO$_2$ per unit photosynthetically active radiation) & $\beta_{\rm lf3}$ &  & \texttt{B\_lf3} & 0.04 \\ 
  Scaling exponent for leaf nitrogen in maximum leaf photosynthesis & $\beta_{\rm lf5}$ &  & \texttt{B\_lf5} & 0.5 \\ 
  \textbf{Respiration} &  &  &  &  \\ 
  CO$_2$ respiration per unit leaf nitrogen & $\beta_{\rm lf4}$ & $\mathrm{mol}\,\mathrm{yr}^{-1}\,\mathrm{kg}^{-1}$ & \texttt{B\_lf4} & 15750 \\ 
  CO$_2$ respiration per unit sapwood volume & $\beta_{\rm rs1}$ & $\mathrm{mol}\,\mathrm{yr}^{-1}\,\mathrm{m}^{-3}$ & \texttt{B\_rs1} & 4012 \\ 
  CO$_2$respiration per unit bark volume & $\beta_{\rm rb1}$ & $\mathrm{mol}\,\mathrm{yr}^{-1}\,\mathrm{m}^{-3}$ & \texttt{B\_rb1} & 8024 \\ 
   \hline
\end{tabular}
\end{table*}

\newpage
\begin{figure*}[!hb]
\centering
\includegraphics[width=0.9\textwidth]{lma_tradeoff.pdf}
\caption{\textbf{Leaf turnover decreases with leaf-mass per unit leaf area.}
Data from \citep{Wright-2004} for 678 species from 51 sites, each
point giving a species-average. Lines show standardised major axis lines
fitted to data from each site, with intensity of shading adjusted
according to strength of the relationship.}
\label{fig:leafturn}
\end{figure*}
\newpage

\begin{figure*}[!hb]
\centering
\includegraphics[width=0.9\textwidth]{assumptions.pdf}
\caption{\textbf{Assumptions of a functional balance model for plant construction.}
Each dot is a single plant from the \textsc{baad} \citep{Falster-2015b}.
Blue lines show standardised major axis lines fit to different species. The black line shows the relationship assumed in this paper, with slope given by the functional-balance assumptions in Table 4 from main text.}
\label{fig:assumptions}
\end{figure*}

@@

\begin{figure*}[!hb]
\centering
\includegraphics[width=0.9\textwidth]{growth_light_dia.pdf}
\caption{\textbf{Effect of four traits on stem-diameter growth rate for different-sized plants.}
Growth rates were simulated using the {\plant} model, applying the trade-offs describing in Table 3. Each panel shows how growth is influenced by a different trait for plants of a given height, and across a series of canopy openness values from completely open (light blue,  $E=1$) to heavily shaded (dark line, $E=0.25$). For any given value of trait and $E$, plants were grown to the desired stem-diameter and their growth rate estimated. Changes in trait-growth relationships are summarised in Table 5.}
\label{fig:growth_light_dia}
\end{figure*}

@@

\begin{figure*}[!hb]
\centering
\includegraphics[width=0.9\textwidth]{growth_light_area.pdf}
\caption{\textbf{Effect of four traits on stem-area growth rate for different-sized plants.}
Growth rates were simulated using the {\plant} model, applying the trade-offs describing in Table 3. Each panel shows how growth is influenced by a different trait for plants of a given height, and across a series of canopy openness values from completely open (light blue,  $E=1$) to heavily shaded (dark line, $E=0.25$). For any given value of trait and $E$, plants were grown to the desired stem-area and their growth rate estimated. Changes in trait-growth relationships are summarised in Table 5.}
\label{fig:growth_light_area}
\end{figure*}

@@

\begin{figure*}[!hb]
\centering
\includegraphics[width=0.9\textwidth]{growth_light_mass.pdf}
\caption{\textbf{Effect of four traits on plant mass growth rate for different-sized plants.}
Growth rates were simulated using the {\plant} model, applying the trade-offs describing in Table 3. Each panel shows how growth is influenced by a different trait for plants of a given height, and across a series of canopy openness values from completely open (light blue,  $E=1$) to heavily shaded (dark line, $E=0.25$). For any given value of trait and $E$, plants were grown to the desired mass and their growth rate estimated. Changes in trait-growth relationships are summarised in Table 5.}
\label{fig:growth_light_mass}
\end{figure*}

>>>>

\documentclass[9pt,twoside]{pnas-new}
% Use the lineno option to display guide line numbers if required.

\templatetype{pnassupportinginfo}

% Use the lineno option to display guide line numbers if required.

\title{How functional traits influence plant growth and shade tolerance across the life-cycle}
\author{Daniel S. Falster Remko A. Duursma, Richard G. FitzJohn}
\correspondingauthor{Corresponding Daniel Falster.\\E-mail: daniel.falster@unsw.edu.au}

@@

\begin{document}

%% Comment/remove this line before generating final copy for submission
%%\instructionspage

@@

%% Adds the main heading for the SI text. Comment out this line if you do not have any supporting information text.
\SItext

\section*{Additional details on the \texttt{FF16} growth model in the {\plant} package}

@@

\subsection*{Hyper-parameterisation of the \texttt{FF16} model via traits}

@@

\subsubsection*{Seed mass}

@@

\subsubsection*{Nitrogen per unit leaf area}

@@

\subsubsection*{Leaf mass per unit area}

@@

\subsubsection*{Wood density}

@@

\subsubsection*{Implementation of hyper-parameterisation function}

@@

% latex table generated in R 3.4.0 by xtable 1.8-2 package
% Thu Apr  5 13:08:59 2018
\begin{table}[ht]
\centering
\caption{Core parameter of the 	exttt{FF16} physiological model.} 
\label{tab:params_core}
\begin{tabular}{p{7cm}llll}
  \hline
Description & Symbol & Unit & Code & Value \\ 
  \hline
\textbf{Plant construction} &  &  &  &  \\ 
  Crown-shape parameter & $\eta$ &  & \texttt{eta} & 12 \\ 
  Leaf mass per area & $\phi$ & $\mathrm{kg}\,\mathrm{m}^{-2}$ & \texttt{lma} & 0.1978791 \\ 
  Wood density & $\rho$ & $\mathrm{kg}\,\mathrm{m}^{-3}$ & \texttt{rho} & 608 \\ 
  Sapwood area per unit leaf area & $\theta$ &  & \texttt{theta} & 0.0002141786 \\ 
  Height of plant with leaf area of 1m$^2$ & $\alpha_{\rm l1}$ & m & \texttt{a\_l1} & 2.17 \\ 
  Exponent of relationship between height and leaf area & $\alpha_{\rm l2}$ &  & \texttt{a\_l2} & 0.5 \\ 
  Root mass per unit leaf area & $\alpha_{\rm r1}$ & $\mathrm{kg}\,\mathrm{m}^{-2}$ & \texttt{a\_r1} & 0.07 \\ 
  Ratio of bark area to sapwood area & $\alpha_{\rm b1}$ &  & \texttt{a\_b1} & 0.17 \\ 
  \textbf{Production} &  &  &  &  \\ 
  Leaf photosynthesis per area & $\alpha_{\rm p1}$ & $\mathrm{mol}\,\mathrm{yr}^{-1}\,\mathrm{m}^{-2}$ & \texttt{a\_p1} & 151.1778 \\ 
  Saturation of leaf photosynthesis per area & $\alpha_{\rm p2}$ &  & \texttt{a\_p2} & 0.2047162 \\ 
  Yield = fraction of carbon fixed converted into mass & $\alpha_{\rm y}$ &  & \texttt{a\_y} & 0.7 \\ 
  Biomass per mol carbon & $\alpha_{\rm bio}$ & $\mathrm{kg}\,\mathrm{mol}^{-1}$ & \texttt{a\_bio} & 0.0245 \\ 
  Leaf respiration per mass & $r_{\rm l}$ & $\mathrm{mol}\,\mathrm{yr}^{-1}\,\mathrm{kg}^{-1}$ & \texttt{r\_l} & 198.4545 \\ 
  Fine-root respiration per mass & $r_{\rm r}$ & $\mathrm{mol}\,\mathrm{yr}^{-1}\,\mathrm{kg}^{-1}$ & \texttt{r\_r} & 217 \\ 
  Sapwood respiration per mass & $r_{\rm s}$ & $\mathrm{mol}\,\mathrm{yr}^{-1}\,\mathrm{kg}^{-1}$ & \texttt{r\_s} & 6.598684 \\ 
  Bark respiration per mass & $r_{\rm b}$ & $\mathrm{mol}\,\mathrm{yr}^{-1}\,\mathrm{kg}^{-1}$ & \texttt{r\_b} & 13.19737 \\ 
  Turnover rate for leaves & $k_{\rm l}$ & $\mathrm{yr}^{-1}$ & \texttt{k\_l} & 0.1521952 \\ 
  Turnover rate for sapwood & $k_{\rm s}$ & $\mathrm{yr}^{-1}$ & \texttt{k\_s} & 0.2 \\ 
  Turnover rate for bark & $k_{\rm b}$ & $\mathrm{yr}^{-1}$ & \texttt{k\_b} & 0.2 \\ 
  Turnover rate for fine roots & $k_{\rm r}$ & $\mathrm{yr}^{-1}$ & \texttt{k\_r} & 1 \\ 
  \textbf{Fecundity} &  &  &  &  \\ 
  Seed mass & $\omega$ & kg & \texttt{omega} & 0.000038 \\ 
  Height at maturation & $H_{{\rm mat}}$ & m & \texttt{hmat} & 15 \\ 
  Maximum allocation to reproduction & $\alpha_{\rm f1}$ &  & \texttt{a\_f1} & 0.8 \\ 
  Parameter determining rate of change in $r(x, m_\textrm{l})$ around $H_{\rm mat}$ & $\alpha_{\rm f2}$ &  & \texttt{a\_f2} & 10 \\ 
   \hline
\end{tabular}
\end{table}

% latex table generated in R 3.4.0 by xtable 1.8-2 package
% Thu Apr  5 13:08:59 2018
\begin{table}[ht]
\centering
\caption{Parameters for hyper-parameterisation of the \texttt{FF16} physiological model.} 
\label{tab:params_hyper}
\begin{tabular}{p{9cm}llll}
  \hline
Description & Symbol & Unit & Code & Value \\ 
  \hline
\textbf{Leaf turnover} &  &  &  &  \\ 
  Global average leaf mass per area & $\phi_0$ & $\mathrm{kg}\,\mathrm{m}^{-2}$ & \texttt{lma\_0} & 0.1978791 \\ 
  Rate of leaf turnover at average leaf mass per unit leaf area, $\phi_0$ & $\beta_{\rm kl1}$ & $\mathrm{yr}^{-1}$ & \texttt{B\_kl1} & 0.4565855 \\ 
  Scaling exponent for $\phi$ in leaf turnover & $\beta_{\rm kl2}$ &  & \texttt{B\_kl2} & 1.71 \\ 
  \textbf{Sapwood turnover} &  &  &  &  \\ 
  Global average wood density & $\rho_0$ & $\mathrm{kg}\,\mathrm{m}^{-3}$ & \texttt{rho\_0} & 608 \\ 
  Rate of sapwood turnover at average wood density, $\rho_0$ & $\beta_{\rm ks1}$ & $\mathrm{yr}^{-1}$ & \texttt{B\_ks1} & 0.2 \\ 
  Scaling exponent for $\rho$ in sapwood turnover & $\beta_{\rm ks2}$ &  & \texttt{B\_ks2} & 1.25 \\ 
  \textbf{Photosynthesis} &  &  &  &  \\ 
  Leaf nitrogen per unit leaf area & $\nu$ & $\mathrm{kg}\,\mathrm{m}^{-2}$ & \texttt{narea} & 0.00187 \\ 
  Global average nitrogen per unit leaf area & $\nu_0$ & $\mathrm{kg}\,\mathrm{m}^{-2}$ & \texttt{narea\_0} & 0.00187 \\ 
  Potential CO$_2$ photosynthesis at average leaf nitrogen, $\nu_0$ & $\beta_{\rm lf1}$ & $\mathrm{mol}\,\mathrm{d}^{-1}\,\mathrm{m}^{-2}$ & \texttt{B\_lf1} & 0.8273474 \\ 
  Curvature of light response curve & $\beta_{\rm lf2}$ &  & \texttt{B\_lf2} & 0.75 \\ 
  Quantum yield of leaf photosynthesis (CO$_2$ per unit photosynthetically active radiation) & $\beta_{\rm lf3}$ &  & \texttt{B\_lf3} & 0.04 \\ 
  Scaling exponent for leaf nitrogen in maximum leaf photosynthesis & $\beta_{\rm lf5}$ &  & \texttt{B\_lf5} & 0.5 \\ 
  \textbf{Respiration} &  &  &  &  \\ 
  CO$_2$ respiration per unit leaf nitrogen & $\beta_{\rm lf4}$ & $\mathrm{mol}\,\mathrm{yr}^{-1}\,\mathrm{kg}^{-1}$ & \texttt{B\_lf4} & 15750 \\ 
  CO$_2$ respiration per unit sapwood volume & $\beta_{\rm rs1}$ & $\mathrm{mol}\,\mathrm{yr}^{-1}\,\mathrm{m}^{-3}$ & \texttt{B\_rs1} & 4012 \\ 
  CO$_2$respiration per unit bark volume & $\beta_{\rm rb1}$ & $\mathrm{mol}\,\mathrm{yr}^{-1}\,\mathrm{m}^{-3}$ & \texttt{B\_rb1} & 8024 \\ 
   \hline
\end{tabular}
\end{table}

\clearpage
\begin{figure}[!hb]
\centering
\includegraphics[width=0.9\textwidth]{lma_tradeoff.pdf}
\caption{\textbf{Leaf turnover decreases with leaf-mass per unit leaf area.}
Data from \citep{Wright-2004} for 678 species from 51 sites, each
point giving a species-average. Lines show standardised major axis lines
fitted to data from each site, with intensity of shading adjusted
according to strength of the relationship.}
\label{fig:leafturn}
\end{figure}
\newpage

\begin{figure}[!hb]
\centering
\includegraphics[width=0.9\textwidth]{assumptions.pdf}
\caption{\textbf{Assumptions of a functional balance model for plant construction.}
Each dot is a single plant from the \textsc{baad} \citep{Falster-2015b}.
Blue lines show standardised major axis lines fit to different species. The black line shows the relationship assumed in this paper, with slope given by the functional-balance assumptions in Table 4 from main text.}
\label{fig:assumptions}
\end{figure}

@@

\begin{figure}[!hb]
\centering
\includegraphics[width=0.9\textwidth]{growth_light_dia.pdf}
\caption{\textbf{Effect of four traits on stem-diameter growth rate for different-sized plants.}
Growth rates were simulated using the {\plant} model, applying the trade-offs describing in Table 3. Each panel shows how growth is influenced by a different trait for plants of a given height, and across a series of canopy openness values from completely open (light blue,  $E=1$) to heavily shaded (dark line, $E=0.25$). For any given value of trait and $E$, plants were grown to the desired stem-diameter and their growth rate estimated. Changes in trait-growth relationships are summarised in Table 5.}
\label{fig:growth_light_dia}
\end{figure}

@@

\begin{figure}[!hb]
\centering
\includegraphics[width=0.9\textwidth]{growth_light_area.pdf}
\caption{\textbf{Effect of four traits on stem-area growth rate for different-sized plants.}
Growth rates were simulated using the {\plant} model, applying the trade-offs describing in Table 3. Each panel shows how growth is influenced by a different trait for plants of a given height, and across a series of canopy openness values from completely open (light blue,  $E=1$) to heavily shaded (dark line, $E=0.25$). For any given value of trait and $E$, plants were grown to the desired stem-area and their growth rate estimated. Changes in trait-growth relationships are summarised in Table 5.}
\label{fig:growth_light_area}
\end{figure}

@@

\begin{figure}[!hb]
\centering
\includegraphics[width=0.9\textwidth]{growth_light_mass.pdf}
\caption{\textbf{Effect of four traits on plant mass growth rate for different-sized plants.}
Growth rates were simulated using the {\plant} model, applying the trade-offs describing in Table 3. Each panel shows how growth is influenced by a different trait for plants of a given height, and across a series of canopy openness values from completely open (light blue,  $E=1$) to heavily shaded (dark line, $E=0.25$). For any given value of trait and $E$, plants were grown to the desired mass and their growth rate estimated. Changes in trait-growth relationships are summarised in Table 5.}
\label{fig:growth_light_mass}
\end{figure}

\newpage
\bibliography{references}
